\tool

### 2017-11-20 paper/paper.tex
Intro updates

\maketitle
\begin{abstract}
Recommendation systems were developed to improve the adoption of useful software tools and features designed to save time and effort in completing tasks that are often ignored by users. Previous research suggests that peer-to-peer recommendations is an effective mode of tool discovery, and the receptiveness of recommendees is a vital characteristic in determining the outcome of tool suggestions. To help increase awareness of useful tools, we developed and evaluated a new system \tool~designed to integrate aspects of peer interactions and user receptivity into automated tool recommendations for software developers of real-world applications. Our findings suggest that \tool~is awesome, cool, and very effective in improving tool discovery.
%Software quality is a primary concern of software engineers and users, however developers often ignore useful tools to improve quality and ease debugging for programmers.
\end{abstract}

@@

\section{Introduction}
%Importance
Software contains many tools and features designed to make users more efficient and effective in their work. However, despite a wide availability of such useful tools, many are often ignored or underutilized because users do not know of their existence. The amount of tools provided by applications is also continuing to increase, making it more difficult for users to discover helpful tools. This lack of awareness can lead to wasted time and billions of wasted dollars each year.

One area where worker effectiveness and efficiency is extremely important is the software industry. Software has permeated nearly every facet of our society and. Additionally, defects and errors in software cost companies millions of dollars to fix.

>>>>

\maketitle
\begin{abstract}
Recommendation systems were developed to improve the adoption of useful software tools and features designed to save time and effort in completing tasks that are often ignored by users. Previous research suggests that peer-to-peer recommendations is an effective mode of tool discovery, and the receptiveness of recommendees is a vital characteristic in determining the outcome of tool suggestions. To help increase awareness of useful tools, we developed and evaluated a new system \tool~designed to integrate aspects of peer interactions and user receptivity into automated tool recommendations for software developers of real-world applications. Our findings suggest that \tool~is awesome, cool, and very effective in improving tool discovery.
\end{abstract}

@@

\section{Introduction}
%Importance
Software contains many tools and features designed to make users more efficient and effective in their work. However, despite a wide availability of such useful tools, many are often ignored or underutilized because users do not know of their existence~\cite{?}. The amount of tools provided by applications is also continuing to increase, making it more difficult for users to discover these helpful tools~\cite{bloat}. This lack of awareness leads to wasted time and billions of wasted dollars each year~\cite{malachowski}.

One area where worker effectiveness and efficiency is extremely important is the software industry. Software has permeated nearly every facet of our society and. Additionally, defects and errors in software cost companies millions of dollars to fix~\cite{?}.
Quality is a primary concern for both software engineers and software users, however developers often ignore useful tools to help improve the quality of their code.
